---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# **rgeomex**

[![Build Status](https://travis-ci.org/pages-themes/cayman.svg?branch=master)](https://travis-ci.org/pages-themes/cayman) [![Gem Version](https://badge.fury.io/rb/jekyll-theme-cayman.svg)](https://badge.fury.io/rb/jekyll-theme-cayman)[![Github All Releases](https://img.shields.io/github/downloads/fdzul/geomex/total.svg)]()

**rgeomex is a package developed in the department of prevention and control of diseases transmitted by vector of the [Secretary of Health of Veracruz](https://www.ssaver.gob.mx/) with colaboration of the [CENAPRECE](https://www.gob.mx/salud/cenaprece) and [INDRE](https://www.gob.mx/salud/acciones-y-programas/instituto-de-diagnostico-y-referencia-epidemiologicos-mision-vision-y-politica-de-calidad-181639?state=published)** 

## **overview**

**rgeomex** is a package to provides spatial dataset (areal data) available and published homepage of [INE](https://pautas.ine.mx/transparencia/mapas/) and [INEGI](https://www.inegi.org.mx/temas/mg). These spatial dataset are useful for visualization and spatial analysis of diseases. The secondary objective of the package is to provide spatial bases for the calculation of dengue hotspots and their vector. the package have six spatial datasets.

  - **`blocks_ine20_mx`** A spatial dataset containing of polygon data of blocks from México (INE 2020).
  - **`localities_inegi19_mx`** A spatial dataset containing of polygon data of localities from México (INEGI 2019).
  - **`AGEB_inegi19_mx`** A spatial dataset containing of polygon data of AGEBs from México (INEGI 2019).
  - **`AGEE_inegi19_mx`** A spatial dataset containing of polygon data of AGEE from México (INEGI 2019).
  - **`AGEM_inegi19_mx`** A spatial dataset containing of polygon data of AGEM from México (INEGI 2019).



## Installation

You can install the released version of geomex from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rgeomex")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fdzul/rgeomex")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, dpi= 300}
library(magrittr)
library(sf)
loc_acapulco <-  rgeomex::loc_inegi19_mx %>%
        dplyr::filter(NOMGEO %in% c(similiars::find_most_similar_string("Acapulco de Juarez", unique(NOMGEO))) &
                          AMBITO %in% c("Urbana"))
plot(sf::st_geometry(loc_acapulco))

ageb_acapulco <- rgeomex::AGEB_inegi_2019_a[loc_acapulco,]
head(ageb_acapulco)
ggplot2::ggplot()+
  ggplot2::geom_sf(data = ageb_acapulco,
                   fill = "gray80",
                   col = "white") +
  ggplot2::theme_void() +
  ggplot2::geom_sf(data = loc_acapulco,
                   fill = NA,
                   col = "black",
                   lwd = .5)




```

## Authors

* **Felipe Antonio Dzul Manzanilla** -**https://github.com/fdzul** - Packages developed in github:

  1) [denhotspots](https://github.com/fdzul/denhotspots). 
  2) [boldenr](https://github.com/fdzul/boldenr). 
  3) [dendata](https://github.com/fdzul/dendata).
  4) [deneggs](https://github.com/fdzul/deneggs).

* **Fabián Correa Morales**
* **Luis Hernández Herrera**
* **Arturo Baez-Hernández**
* **Evaristo Morales Ríos**
* **Heron Huerta**



See also the list of [contributors](https://github.com/fdzul/geomex/contributors) who participated in this project.

## License

This project is licensed under the MIT License - see the [LICENSE.md](LICENSE.md) file for details


## Inspiration

The package was inspired by the need to contribute to making decisions in the dengue prevention and control program, specifically to identify dengue vector hotspots and use the entomological information generated by the program.

## Getting help

If you encounter a clear bug, please file a minimal reproducible example
on [github](https://github.com/fdzul/rgeomex/issues). For questions
and other discussion, please feel free to contact me (felipe.dzul.m@gmail.com)

-----

Please note that this project is released with a [Contributor Code of
Conduct](https://dplyr.tidyverse.org/CODE_OF_CONDUCT). By participating
in this project you agree to abide by its terms.
